\documentclass[11pt]{article}
\input{resformat.tex}

\begin{document}
\myHeader{Thomas Varano}
% contact
\vspace{-3mm}
\begin{center}
    \contactItem{thvarano@gmail.com}{mailto:thvarano@gmail.com} |
    \contactItem{tomvarano.com}{https://tomvarano.com} |
    \contactItem{(201) 887-3953}{tel:2018873953} |
    \contactItem{linkedin.com/in/thomas-varano/}{https://linkedin.com/in/thomas-varano} |
    \contactItem{github.com/tvarano}{https://github.com/tvarano} 
\end{center}
\bighsep[1pt]

% top row
\begin{tabular}[t]{l | l}
    \hspace{-8mm}
    \noindent\parbox[t][][t]{0.3\textwidth}{
        % education
        \setlength\topsep{1pt}
        \sechead{Education}
        {\fontsize{9}{12}\robotocondlight
        \begin{itemize}[noitemsep, topsep=0pt, label={}, leftmargin=*]
            \item University of Maryland – College Park
            \item BS / MS Computer Science Program
            \item Minor in Mathematics
            \item Graduation: May 2023, BS in 2022
            \item  GPA: 3.95 
        \end{itemize}
        }
    }
    &
    \parbox[t][][t]{0.4\textwidth}{
        % Relevant Coursework
        \sechead{Coursework}
        {\fontsize{9}{12}\robotocondlight
        \noindent\begin{tabularx}{\textwidth}[t]{l l l}
            \courseentry{Object Oriented Programming II} & \courseentry{Applications of Linear Algebra}\\
            \courseentry{Linear Algebra} & \courseentry{Organization of Programming Languages}\\
            \courseentry{Discrete Structures} & \courseentry{Intro to Computer Systems} \\ \courseentry{Calculus III} & \courseentry{Algorithms}
        \end{tabularx}
        }
    }
    
\end{tabular}
\hsep[1pt]
\vspace{-2mm}

% skills
\setlength\topsep{0pt}
\sechead{Relevant Skills}
{
    {\fontsize{10}{12}\robotocondlight
        15 years of Skiing, CPR Certified, Excellent Interpersonal Skills, Teaching Experience
    }
}

\hsep

% Experience
\sechead{Experience}
\vspace{2mm}
{\fontsize{10}{12}\robotocondlight
% TA
    \expheader{Teaching Assistant}{University of Maryland}{August 2020}{Present}
    \begin{itemize}[noitemsep,nolistsep]
        \item Act as office hours and grading teaching assistant for CMSC 132 (Object Oriented Programming II).
        \item Hold virtual office hours for students, teaching data structures in Java and helping students debug projects.
    \end{itemize}
    \vspace{3mm}

% Fidelity
    \expheader{IT Intern}{Fidelity National Financial}{July 2020}{August 2020}
    \begin{itemize}[noitemsep,nolistsep]
        \item Imaged devices, set up workstations, configured print servers. 
        \item Troubleshot various server and user issues either in person or over remote connection.
        \item Learned intricacies of numerous software programs regarding installation, troubleshooting, and repair, maintaining the effectiveness of coworkers. 
    \end{itemize}
    \vspace{3mm}
% PHHS
    \expheader{Teaching Assistant}{Pascack Hills High School}{Sept 2018}{June 2019}
    \begin{itemize}[noitemsep,nolistsep]
        \item Taught students fundamental programming techniques, focusing on Java. Helped debug and analyze students’ projects. 
        \item Co-found and develop curriculum for Advanced Topics in Computer Science, a class teaching Python, webdev, Swift, and Arduino, among other subjects. 
    \end{itemize}
    \vspace{3mm}
    \expheader{Kitchen Manager}{Life Time Athletic}{May 2017}{January 2020}
    \begin{itemize}[noitemsep,nolistsep]
        \item Managed a team to efficiently operate a bistro kitchen. 
        \item Coordinated with members and other managers to ensure coverage of timesheet, adequate ordering of produce, and prevention of waste.
    \end{itemize}
    \vspace{3mm}
    \expheader{Soccer Referee}{Montvale Athletic League}{August 2015}{December 2017}
    \begin{itemize}[noitemsep,nolistsep]
        \item Refereed recreational soccer games, age 6-15. 
        \item Coordinated with other referees for scheduling and score reporting.
    \end{itemize}
    \vspace{3mm}

\vspace{-2mm}
{\fontsize{8}{10}\robotocondlight References available upon request.}
}
\hsep


% Activities
\sechead{Activities / Leadership}
{\fontsize{10}{12}\robotocondlight
\noindent Open Sourcery
\begin{itemize}[noitemsep,nolistsep]
    \item Computer Science club specializing in open source cooperation and contribution. Weekly meetings either involve workshops on varying 
    technologies or breakoffs where different groups within the club discuss and work on their own team projects. 
    \item Acting Personal Relations Officer, fielding member questions, running social media, sending announcements, 
    and spearheading outreach for new members.
\end{itemize}
Sigma Phi Delta
\begin{itemize}[noitemsep,nolistsep]
    \item Engineering Fraternity
    \item Engage and Network with other Engineers / Computer Science Majors.
    \item Build a network of support both in and out of the classroom.
\end{itemize}
CompuTerps
\begin{itemize}[noitemsep,nolistsep]
    \item Computer Science Discussion Club
    \item Discuss popular topics in technology, from both a consumer and developer perspective. 
\end{itemize}
Terrapin Ski Club, Running Club, University Jazz Band, UMD Spikeball Club
}
\end{document}
