\documentclass[11pt]{article}
\input{resformat.tex}

\begin{document}
\myHeader{Thomas Varano}{Computer Science Student}
\bighsep[1pt]

% top row

\begin{tabular}[t]{r | l | l}
    \parbox[t][][t]{0.2\textwidth}{
        % contact
        \setlength\topsep{0pt}
        \hspace{-8mm}
        \sechead{Contact}
        \begin{flushright}
            \contactItem{thvarano@gmail.com}{mailto:thvarano@gmail.com}{mail}
            \contactItem{tomvarano.com}{https://tomvarano.com}{link}
            \contactItem{(201) 887-3953}{tel:2018873953}{phone}
            \contactItem{/in/thomas-varano}{https://linkedin.com/in/thomas-varano}{linkedin}
            \contactItem{github.com/tvarano}{https://github.com/tvarano}{github}
        \end{flushright}
    }
    &
    \parbox[t][][t]{0.3\textwidth}{
        % education
        \setlength\topsep{1pt}
        \sechead{Education}
        {\fontsize{9}{12}\robotocondlight
        University of Maryland – College Park\par
        Bachelor’s in Computer Science\par
        Minor in Mathematics\par
        Graduation: May 2023\par
        GPA: 3.95 \hspace{18mm} ACT:34\par
        SAT Math II: 800 \hspace{10mm} SAT Physics: 740
        }
    }
    &
    \parbox[t][][t]{0.48\textwidth}{
        % skills
        \setlength\topsep{0pt}
        \sechead{Skills}
        {\fontsize{9}{12}\robotocondlight
        \begin{tabular}[t]{r l}
            Java & C\\
            JavaScript & Assembly (MIPS)\\
            Python & BASH / tcsh\\
            Git & \LaTeX\\
            HTML / CSS & Windows / MacOS / Linux
        \end{tabular}
        }
    }
\end{tabular}
\hsep[1pt]
\vspace{-2mm}

% Relevant Coursework
\sechead{Relevant Coursework}
\vspace{2mm}
{\fontsize{9}{12}\robotocondlight
\noindent\begin{tabularx}{\textwidth}[t]{r L  r L  r L}
    \courseentry{CMSC 132}{OOP II} & \courseentry{MATH 241}{Calculus III} & \courseentry{MATH 401}{Applications of Linear Algebra}\\
    \courseentry{MATH 240}{Linear Algebra}
    & \courseentry{ENES 210}{\multirow[t]{3}{=}{Entrepreneurial Opportunity Analysis and Decision-Making  in Technology Ventures}}
    & \courseentry{CMSC 330}{\multirow[t]{3}{=}{Organization of Programming Languages}}\\
    \courseentry{CMSC 250}{Discrete Structures} \\
    \courseentry{CMSC 216}{Intro to Computer Systems} & \emptycourse & \courseentry{CMSC 351}{Algorithms}
\end{tabularx}
}
\vspace{-3mm}
\hsep
\vspace{-3mm}

% Projects
\sechead{Projects}
\vspace{2mm}
\projectheader{Ocean Pollution Analyzer}{Competition Project}{2020}
{\fontsize{10}{12}\robotocondlight
\begin{itemize}[noitemsep,nolistsep]
    \item A UMD Data Challenge project analyzing Booz Allen Hamilton data on ocean pollution cleanups. 
    \item Hosted a {\robotocond Python flask} webapp to illustrate the effectiveness of cleanups and which places were reported to have the most pollution. 
    \item Created and accessed a {\robotocond SQLite} database with SQLite to analyze over 45,000 rows of data.
\end{itemize}
\projectheader{Portfolio Site}{Personal Project}{2019-2020}
{\fontsize{10}{12}\robotocondlight
\begin{itemize}[noitemsep,nolistsep]
    \item Created and maintained a website holding resume, contact, and bio information.
    \item Used {\robotocond HTML}, {\robotocond CSS}, {\robotocond jQuery}, and {\robotocond Python} to host on {\robotocond Google Cloud}.
\end{itemize}
\projectheader{Career Day}{School Project}{2018-2019}
\begin{itemize}[noitemsep,nolistsep]
    \item Sorted 800 students to their preferred Career Day speakers in accordance with their top choices and an assortment of variables.
    \item Lead a team of 12 student programmers in {\robotocond Java} and {\robotocond Python} using {\robotocond Git} to merge different groups’ code to a final project.
\end{itemize}
\projectheader{Agenda}{Personal Project}{2017-2018}
\begin{itemize}[noitemsep,nolistsep]
    \item Kept track of rotating schedules, labs, GPA, and time management for high school students. 
    \item Released an app for OSX, iOS, and web, using {\robotocond Java}, {\robotocond Swift},
     and {\robotocond HTML}, {\robotocond CSS}, {\robotocond JS}, and {\robotocond Python} respectively
\end{itemize}
{\fontsize{8}{10}\robotocondlight Project links: tomvarano.com/about \hfill Github: github.com/tvarano
}
\vspace{-5mm}
\hsep
\vspace{-3mm}

% Experience
\sechead{Experience}
\vspace{2mm}
{\fontsize{10}{12}\robotocondlight
% TA
    \expheader{Teaching Assistant}{CMSC 132}{University of Maryland}{August 2020}{Present}
    \begin{itemize}[noitemsep,nolistsep]
        \item Act as office hours and grading teaching assistant for CMSC 132 (Object Oriented Programming II).
        \item Hold virtual office hours for students, teaching data structures in Java and helping students debug projects.
    \end{itemize}
    \vspace{3mm}

% Fidelity
    \expheader{IT Intern}{Fidelity National Title}{Fidelity National Financial}{July 2020}{August 2020}
    \begin{itemize}[noitemsep,nolistsep]
        \item Imaged devices, set up workstations, configured print servers. 
        \item Troubleshot various server and user issues either in person or over remote connection.
        \item Learned intricacies of numerous software programs regarding installation, troubleshooting, and repair, maintaining the effectiveness of coworkers. 
    \end{itemize}
    \vspace{3mm}
% PHHS
    \expheader{Teaching Assistant}{APCS}{Pascack Hills High School}{Sept 2018}{June 2019}
    \begin{itemize}[noitemsep,nolistsep]
        \item Taught students fundamental programming techniques, focusing on Java. Helped debug and analyze students’ projects. 
        \item Co-found Advanced Topics in Computer Science class, with curriculum involving Python, webdev, Swift, and Arduino. 
    \end{itemize}
    \vspace{3mm}

\vspace{-2mm}
{\fontsize{8}{10}\robotocondlight References available upon request.}
}
\vspace{-5mm}
\hsep
\vspace{-3mm}

% Activities
\sechead{Activities / Leadership}
{\fontsize{10}{12}\robotocondlight
\noindent Open Sourcery
\begin{itemize}[noitemsep,nolistsep]
    \item Computer Science club specializing in open source cooperation and contribution. Weekly meetings either involve workshops on varying 
    technologies or breakoffs where different groups within the club discuss and work on their own team projects. 
    \item Acting Personal Relations Officer, fielding member questions, running social media, sending announcements, 
    and spearheading outreach for new members.
\end{itemize}
Sigma Phi Delta
\begin{itemize}[noitemsep,nolistsep]
    \item Professional / Social Engineering Fraternity
\end{itemize}
CompuTerps
\begin{itemize}[noitemsep,nolistsep]
    \item CS Discussion Club
\end{itemize}
}
\end{document}
