\documentclass[11pt]{article}
\input{resformat.tex}

\begin{document}
\myHeader{Thomas Varano}
% contact
\vspace{-3mm}
\begin{center}
    \contactItem{thvarano@gmail.com}{mailto:thvarano@gmail.com} |
    \contactItem{tomvarano.com}{https://tomvarano.com} |
    \contactItem{(201) 887-3953}{tel:2018873953} |
    \contactItem{linkedin.com/in/thomas-varano/}{https://linkedin.com/in/thomas-varano} |
    \contactItem{github.com/tvarano}{https://github.com/tvarano} 
\end{center}
\bighsep[1pt]

% top row
\begin{tabular}[t]{l | l}
    \hspace{-8mm}
    \noindent\parbox[t][][t]{0.3\textwidth}{
        % education
        \setlength\topsep{1pt}
        \sechead{Education}
        {\fontsize{9}{12}\robotocondlight
        \begin{itemize}[noitemsep, topsep=0pt, label={}, leftmargin=*]
            \item University of Maryland – College Park
            \item BS Computer Science
            \item Minor in Mathematics
            \item Graduation: May 2022
            \item GPA: 3.95 
        \end{itemize}
        }
    }
    &
    \parbox[t][][t]{0.4\textwidth}{
        % Relevant Coursework
        \sechead{Relevant Coursework}
        {\fontsize{9}{12}\robotocondlight
        \noindent\begin{tabularx}{\textwidth}[t]{l l l}
            % Linear Algebra Discrete Structures
            \courseentry{Object Oriented Programming II} & \courseentry{Linear Algebra} & \courseentry{Intro to Computer Systems} \\
            \courseentry{Discrete Structures} & \courseentry{Calculus III} & \courseentry{Organization of Programming Languages} \\
            \courseentry{Applications of Linear Algebra} & \courseentry{Algorithms} & \courseentry{Advanced Data Structures} \\
            \courseentry{Applied Probability and Statistics} & \courseentry{Intro to Data Science} & \courseentry{Analysis of Computer Algorithms} \\
            \courseentry{Intro to Machine Learning} & \courseentry{Computer Networks} & \courseentry{Advanced Calculus I}
        \end{tabularx}
        }
    }
    
\end{tabular}
\hsep[1pt]
\vspace{-2mm}

% skills
\setlength\topsep{0pt}
\sechead{Skills}
{\fontsize{10}{12}\robotocondlight
    \noindent{\robotocond Programming Languages (Proficient:)} Python, Swift, Java \quad {\robotocond (Experience:)} JavaScript, BASH, C, SQLite, OCaml, Ruby, , Assembly (MIPS), Rust \par
    \noindent{\robotocond Technologies:}
    Git, XCTest, \LaTeX, HTML / CSS, Flask, Google Cloud, Heroku, JUnit, Jupyter, VSCode, Vim, Windows, MacOS, Linux \par
}

\hsep

% Experience
\sechead{Experience}
\vspace{2mm}4
{\fontsize{10}{12}\robotocondlight
% Apple
    \expheader{Software Engineering Intern}{Apple}{May 2021}{August 2021}
    \begin{itemize}[noitemsep,nolistsep]
        \item Validate syncing capabilities of the Shortcuts app on iOS and macOS. 
        \item Quickly comprehend and navigate expansive codebase, developing new tests and improving structure they are built on. 
        \item Develop MultiDevice testing approach to sync multiple devices in a test run, using Swift to run custom Test Plans.
        \item Triage test results, report specific failures to Shortcuts developers to improve product to ship.
    \end{itemize}
    \vspace{3mm}
% TA
    \expheader{Teaching Assistant}{University of Maryland}{August 2020}{Present}
    \begin{itemize}[noitemsep,nolistsep]
        \item Teach student-let course CMSC 389O, The Coding Interview. Teach students techniques for behavioral and technical interviews. 
        \item Act as office hours and grading teaching assistant for CMSC 132, Object Oriented Programming II.
        \item Hold virtual office hours for students, teaching data structures in Java and helping students debug projects.
    \end{itemize}
    \vspace{3mm}

% Fidelity
    \expheader{IT Intern}{Fidelity National Financial}{July 2020}{August 2020}
    \begin{itemize}[noitemsep,nolistsep]
        \item Imaged devices, set up workstations, configured print servers. 
        \item Troubleshot various server and user issues either in person or over remote connection.
        \item Learned intricacies of numerous software programs regarding installation, troubleshooting, and repair, maintaining the effectiveness of coworkers. 
    \end{itemize}
    \vspace{3mm}
% PHHS
    % \expheader{Teaching Assistant}{Pascack Hills High School}{Sept 2018}{June 2019}
    % \begin{itemize}[noitemsep,nolistsep]
    %     \item Taught students fundamental programming techniques, focusing on Java. Helped debug and analyze students’ projects. 
    %     \item Co-found Advanced Topics in Computer Science class, with curriculum involving Python, webdev, Swift, and Arduino. 
    % \end{itemize}
    % \vspace{3mm}

\vspace{-2mm}
{\fontsize{8}{10}\robotocondlight References available upon request.}
}
\hsep


% Projects
\sechead{Projects}
\vspace{2mm}
\projectheader{MultiDevice Testing}{Intern Project}{2021}
{\fontsize{10}{12}\robotocondlight
\begin{itemize}[noitemsep,nolistsep]
    \item Intern project to improve Multi Device testing at Apple. 
    \item Create a new approach for Multi Device testing, generalized to be used on multiple platforms for multiple different Apple products. 
    \item Create a suite of tests in {\robotocond Swift} using {\robotocond XCodeUI Tests} for the Shortcuts app, programmatically verifying the app's syncing feature.
    \item Run newly created tests in CI environment for Presubmission testing.
    \item Thoroughly document project for ease of use across teams and software implementations.
\end{itemize}
\projectheader{Top Hits Analyzer}{School Project}{2021}
\begin{itemize}[noitemsep,nolistsep]
    \item A Data Science project analyzing and categorizing trends of Billboard top hits. 
    \item Clean and parse over 325k entries of songs on the BillBoard Hot 100 using {\robotocond pandas} and {\robotocond numpy}.
    Create K-Means model using {\robotocond scikitlearn} and place songs into categories depending on how they trended on the chart. 
\end{itemize}
\projectheader{Offset}{Competition Project}{2021}
\begin{itemize}[noitemsep,nolistsep]
    \item A Bitcamp hackathon project analyzing the carbon footprint of consumer deliveries and online shopping. 
    \item Parse package tracking numbers from user's Gmail using {\robotocond Python} API. 
    \item Reverse engineer APIs to gather information about packages and their exact carbon impacts. 
    \item Use {\robotocond Python Flask} to host a website querying all endpoints and displaying information to user.
\end{itemize}
% \projectheader{Ocean Pollution Analyzer}{Competition Project}{2020}
% \begin{itemize}[noitemsep,nolistsep]
%     \item A UMD Data Challenge project analyzing Booz Allen Hamilton data on ocean pollution cleanups. 
%     \item Hosted a {\robotocond Python flask} webapp to illustrate the effectiveness of cleanups and which places were reported to have the most pollution. 
%     \item Created and accessed a {\robotocond SQLite} database to analyze over 45,000 rows of data.
% \end{itemize}
% \projectheader{Portfolio Site}{Personal Project}{2019-2020}
% \begin{itemize}[noitemsep,nolistsep]
%     \item Created and maintained a website holding resume, contact, and bio information.
%     \item Used {\robotocond HTML}, {\robotocond CSS}, {\robotocond jQuery}, and {\robotocond Python} to host on {\robotocond Google Cloud}.
% \end{itemize}
% \projectheader{Career Day}{School Project}{2018-2019}
% \begin{itemize}[noitemsep,nolistsep]
%     \item Sorted 800 students to their preferred Career Day speakers in accordance with their top choices and an assortment of variables.
%     \item Lead a team of 12 student programmers in {\robotocond Java} and {\robotocond Python} using {\robotocond Git} to merge different groups’ code to a final project.
%     \item Acted as Project Manager, assigning tickets, bugs, and features, while also working on the project firsthand.
% \end{itemize}
}
{\fontsize{8}{10}\robotocondlight Project links: tomvarano.com/about \hfill Github: github.com/tvarano
}
\hsep
% Activities
\sechead{Activities / Leadership}
{\fontsize{10}{12}\robotocondlight
\noindent Open Sourcery
\begin{itemize}[noitemsep,nolistsep]
    \item Computer Science club specializing in open source cooperation and contribution. Weekly meetings either involve workshops on varying 
    technologies or breakoffs where different groups within the club discuss and work on their own team projects. 
\end{itemize}
Sigma Phi Delta
\begin{itemize}[noitemsep,nolistsep]
    \item Engineering Fraternity
    \item Assistant Treasurer: Delegate spending, budget income across projects and events.
    \item Risk Manager: Mitigize Covid risk and ensure all events adhere to Covid guidelines. 
    \item Engage and Network with other Engineers / Computer Science Majors.
\end{itemize}
Running Club, University Jazz Band, Terrapin Ski Club, UMD Spikeball Club
}
\end{document}
